---
title: "index.rmd"
author: "Carolyn"
date: "11/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(httr)
library(dplyr)
source("analysis.R")
```

## Information

In the past year, there were a total of `r num.shootings` of shootings that occurred and a total of `r num.killed` lives were lost. The most impacted cities (more than 5 people killed in one shooting) were `r impacted.list`. The city with the most number of lives lost in a single shooting was `r most.killed$city` on `r most.killed$date` with a total of `r most.killed$killed` lives lost.  

```{r cars, echo=FALSE}
library(plotly)
library(dplyr)

kable(s.table)

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB('gray'),
  subunitwidth = 1,
  countrywidth = 1,
  subunitcolor = toRGB("white"),
  countrycolor = toRGB("gray")
)

plot_geo(shootings.data, locationmode = 'USA-states') %>%  
  layout(title = 'Shootings data in USA', geo = g) %>%  
  add_markers(x = ~lng, y = ~lat, color = ~killed, size = ~killed, text = ~paste(shootings.data$state, "<br />", shootings.data$killed, " killed")
              )  

plot_ly(s.table, x = ~state, y = ~sum.injured, type = 'bar', name = 'Total injured') %>%
  add_trace(y = ~s.table$sum.killed, name = 'Total killed') %>%
  layout(margin = list(b = 160), width = 800, yaxis = list(title = 'Casualty count'), barmode = 'stack')


```

## `r incident.city` Shooting

On `r incident.date`, there was a shooting in `r incident.city`, `r incident.state`. According to [CNN](http://www.cnn.com/2017/10/12/us/las-vegas-shooting-investigation-updates/index.html), Las Vegas gunman Stephen Paddock opened fire on a crowd at a music festival just 40 seconds after shooting a Mandalay Bay Resort and Casino security guard. In this incident, `r incident.killed` people were killed and `r incident.injured` were left injured. The gunman later took his own life in his hotel room. 




