---
title: "index.rmd"
author: "Carolyn"
date: "11/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(httr)
library(dplyr)
source("analysis.R")
```

## Information

In the past year, there were a total of `r num.shootings` of shootings that occurred and a total of `r num.killed` lives were lost. The most impacted cities (more than 5 people killed in one shooting) were `r impacted.list`. The city with the most number of lives lost in a single shooting was `r most.killed$city` on `r most.killed$date` with a total of `r most.killed$killed` lives lost.  

```{r cars, echo=FALSE}
library(plotly)
library(dplyr)

kable(s.table)

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB('gray'),
  subunitwidth = 1,
  countrywidth = 1,
  subunitcolor = toRGB("white"),
  countrycolor = toRGB("gray")
)

plot_geo(shootings.data, locationmode = 'USA-states') %>%  
  layout(title = 'Shootings data in USA', geo = g) %>%  
  add_markers(x = ~lng, y = ~lat, color = ~killed, size = ~killed, text = ~paste(shootings.data$state, "<br />", shootings.data$killed, " killed")
              )  

plot_ly(s.table, x = ~state, y = ~sum.injured, type = 'bar', name = 'Total injured') %>%
  add_trace(y = ~s.table$sum.killed, name = 'Total killed') %>%
  layout(margin = list(b = 160), width = 800, yaxis = list(title = 'Casualty count'), barmode = 'stack')


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
